---
title: "Week 7 Assignment"
author: "Al Haque"
date: "3/16/2022"
output: html_document
---

## Info: 
 The task is to convert an html file,json and xml file into a dataframe into R at first I wasnt sure how to read the files from the web so I did read it locally.But I later tailored each file for reproducibility, so I put the files into Github and I used the readlines function to read the raw data and then I parsed each file to its specific function i.e html file to htmlparse, xml file to xml parse and json file to Fromjson. From there I did my best to convert the information into a R data_frame 

```{r}

## converting html page to a R data frame
## wasn't sure how to read the direct html file since I used sublime text edit to make the html so I used readLines to read from the raw data from Github 
library(XML)
library(jsonlite)
library(dplyr)
url <- readLines("https://raw.githubusercontent.com/AldataSci/Data607Week7Assignment/main/table.html")
parsed_detail <- htmlParse(url)

tables <- readHTMLTable(url)
table <- as.data.frame(tables)
table
```

```{r}
## getting an xml file using xmlToDataFrame to convert an xml file into a Data Frame 
URL <- readLines("https://raw.githubusercontent.com/AldataSci/Data607Week7Assignment/main/book.xml")
book_xml <- xmlParse("C://Users//Al Haque//Desktop//AL Info Folder//book.xml")
book <-xmlToDataFrame(book_xml)
book
```

```{r}
##json file.
## converting a json file into a Data Frame
link <- "https://raw.githubusercontent.com/AldataSci/Data607Week7Assignment/main/book.json"
book_json <- fromJSON(link) %>%
  as.data.frame()
book_json
```

